\myfont Implementation and evaluation of register allocation used to translate LLVM-{}- to x86-64

### 2024-01-07 article.tex
Attempt to readjust width of graphs
Display resulting assignments
Talk a bit more about coalescing

% Side by side figures 
\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=10em]{countdown.simple2}
      \caption{Graph}\label{fig:countdown.dot2}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
        \texttt{\%c1}
        \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack2}
    \end{subfigure}
    \caption{Push \texttt{\%c1}}
  \end{minipage}%
  \begin{minipage}[b]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=10em]{countdown.simple3}
      \caption{Graph}\label{fig:countdown.dot3}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
        \texttt{\%argv}\\
        \texttt{\%c1}
        \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack3}
    \end{subfigure}
    \caption{Push \texttt{\%argv}}
  \end{minipage}%
  \begin{minipage}[b]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple4}
      \caption{Graph}\label{fig:countdown.dot4}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \caption{Stack}\label{fig:countdown.stack4}
    \end{subfigure}
    \caption{Spill \texttt{\%c2}}
  \end{minipage}%
\end{figure}
\noindent From this point onwards  nothing can be done to further simplify the graph as all of the remaining nodes are of significant degree (\(\geq 2\)). Therefore, one of the remaining nodes is spilled to memory and entirely removed from the graph as can be seen on Figure \ref{fig:countdown.dot4} and the stack reset as can be seen on Figure \ref{fig:countdown.stack4}.

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple11} 
      \caption{Graph}\label{fig:countdown.dot11}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack11}
    \end{subfigure}
    \caption{Pop \texttt{\%argv}} \label{fig:countdown11}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple12} 
      \caption{Graph}\label{fig:countdown.dot12}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \caption{Stack}\label{fig:countdown.stack12} 
    \end{subfigure}
    \caption{Pop \texttt{\%c1}}\label{fig:countdown12} 
  \end{minipage}%
\end{figure}

@@

Since all edges are preserved, the resulting node \(ab\) may be of a much higher degree. Because of this, only strategies that produce a \(k\)-colorable graph are worth considering, as additional spills negate the purpose entirely.

>>>>

% Side by side figures 
\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.31\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=10em]{countdown.simple2}
      \caption{Graph}\label{fig:countdown.dot2}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
        \texttt{\%c1}
        \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack2}
    \end{subfigure}
    \caption{Push \texttt{\%c1}}
  \end{minipage}%
  \begin{minipage}[b]{0.31\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=10em]{countdown.simple3}
      \caption{Graph}\label{fig:countdown.dot3}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
        \texttt{\%argv}\\
        \texttt{\%c1}
        \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack3}
    \end{subfigure}
    \caption{Push \texttt{\%argv}}
  \end{minipage}%
  \begin{minipage}[b]{0.31\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple4}
      \caption{Graph}\label{fig:countdown.dot4}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \caption{Stack}\label{fig:countdown.stack4}
    \end{subfigure}
    \caption{Spill \texttt{\%c2}}
  \end{minipage}%
\end{figure}
\noindent From this point onwards  nothing can be done to further simplify the graph as all of the remaining nodes are of significant degree (\(\geq 2\)). Therefore, one of the remaining nodes is spilled to memory and entirely removed from the graph as can be seen on Figure \ref{fig:countdown.dot4} and the stack reset as can be seen on Figure \ref{fig:countdown.stack4}.

@@

\begin{figure}[H]
  \centering
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple11} 
      \caption{Graph}\label{fig:countdown.dot11}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack11}
    \end{subfigure}
    \caption{Pop \texttt{\%argv}} \label{fig:countdown11}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple12} 
      \caption{Graph}\label{fig:countdown.dot12}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \caption{Stack}\label{fig:countdown.stack12} 
    \end{subfigure}
    \caption{Pop \texttt{\%c1}}\label{fig:countdown12} 
  \end{minipage}%
\end{figure}
\noindent The final coloring of Figure \ref{fig:countdown12} leads to the assignment 
\begin{align*}
  \mathit{assign[\texttt{\%argv}]} = \mathit{assign[\texttt{\%c1}]} = \mathit{assign[\texttt{\%cn}]} &= \texttt{\%red}\\
  \mathit{assign[\texttt{\%argc}]} &= \texttt{\%blue}
\end{align*}
and the spilled variable \texttt{\%c2}
\[
  \mathit{assign[\texttt{\%c2}]} = \texttt{stackslot(0)}
\]

@@

Since all edges are preserved, the resulting node \(ab\) may be of a much higher degree. Because of this, only strategies that produce a \(k\)-colorable graph are worth considering, as additional spills negate the purpose entirely. One of the  strategies introduced in the Appel text is the \textit{Briggs} strategy  \cite[232]{tiger}, in which nodes \(a\) and \(b\) can be coalesced if and only if the resulting node \(ab\) is of insignificant degree  (i.e. \(\leq K\)).

Since the only move operations in use in LLVM-{}- are phi nodes, only variables that are subject to this sort of operation are eligible to be coalesced in this form. 
Variables that may be coalesced can be thought of as having a different sort of edge, quite the opposite of interference edges, in fact they can be thought of as a sort of 'preference edge'.
Strictly speaking, one could optimize many more mov instructions away if
